mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-21 Draft3.Rmd
aestetics

t <- cbind(Operator=op1, Output=m1, Operator=op2, Output=m2)
knitr::kable(t, caption="Custom operators in mathml", 
             row.names=FALSE, escape=FALSE)
```

@@

op2 <- list(
  twosidearrow=quote(x%<->%b),
  rightarrow=quote(x%->%y),
  leftarrow=quote(x%<-%y),
  uparrow=quote(x%up%y),
  down=quote(x%down%y),
  iff=quote(x%<=>%y),
  rArr=quote(x %=>% y),
  lArr=quote(x %<=% y),
  dblup=quote(x %dblup% y),
  dbldown=quote(x %dbldown% y))
m2 <- lapply(op2, FUN=mathout, flags=list(cat=FALSE))

t <- cbind(Operator=op1, Output=m1, Operator=op2, Output=m2)
knitr::kable(t, caption="Basic elements in mathml", row.names=FALSE, escape=FALSE)
```

@@

```{r, results='asis'}
f <- function(x)
{
  if(x == 0) return(0L);
  if(x <= 0) return(-1L);
  if(x > 0) return(1L)
}

>>>>

op3 <- list(
  twosidearrow=quote(x%<->%b),
  rightarrow=quote(x%->%y),
  leftarrow=quote(x%<-%y),
  uparrow=quote(x%up%y),
  down=quote(x%down%y),
  iff=quote(x%<=>%y),
  rArr=quote(x %=>% y),
  lArr=quote(x %<=% y),
  dblup=quote(x %dblup% y),
  dbldown=quote(x %dbldown% y))
m3 <- lapply(op3, FUN=mathout, flags=list(cat=FALSE))

op3 <- as.character(op3)
if(knitr::is_latex_output())
  op3 <- sapply(op3, FUN=knitr:::escape_latex)
if(knitr::is_html_output())
  op3 <- sapply(op3, FUN=knitr:::escape_html)

t <- cbind(Operator=op1, Output=m1, Operator=op2, Output=m2, Operator=op3, Arrow=m3)
knitr::kable(t, caption="Custom operators in mathml", 
             row.names=FALSE, escape=FALSE)
```

@@

t <- cbind(Function=op1, Output=m1)
knitr::kable(t, caption="Arithmetic functions", row.names=FALSE, escape=FALSE)
```

@@

```{r, results='asis'}
f <- function(x)
{
  if(x == 0L) return(0L);
  if(x <= 0L) return(-1L);
  if(x > 0L) return(1L)
}
